Reionization Planck 2018 Notes

### 2020-07-02 results/notes.tex
Updates from Overleaf

\begin{figure}
\includegraphics[width=0.65\textwidth]{cosmomc_kde/direct_mcmc_vs_python_kde_and_cosmomc_kde_tanh_tau.png}
\caption{LATEST (to be debugged) -- Added cosmomc KDE version of tau posterior computed with f = 0.14, against python versions with f = 0.1, 0.12, 0.14. They do not agree ... (Note: need to make sure python version had the same covariance matrix, and length of chain ... should probably rerun python version actually.)
}
\label{fig:}s
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=0.65\textwidth]{cosmomc_kde/direct_mcmc_vs_python_kde_and_cosmomc_kde_tanh_tau.png}
\caption{LATEST (to be debugged) -- Added cosmomc KDE version of tau posterior computed with f = 0.14, against python versions with f = 0.1, 0.12, 0.14. They do not agree ... (Note: need to make sure python version had the same covariance matrix, and length of chain ... should probably rerun python version actually.)
}
\label{fig:}
\end{figure}

\begin{figure}
\includegraphics[width=0.65\textwidth]{cosmomc_kde/pl18_relike_tanh_tau_dz0p5_1D_direct_vs_fortran_and_python_kde.png}
\caption{DEBUGGING - updated the KDE tanh results to have tanh dz = 0.5. Also added in faint blue lines Gaussian and convolved Gaussian with $\sigma \rightarrow \sigma$.
}
\label{fig:}
\end{figure}

\begin{figure}
\includegraphics[width=0.65\textwidth]{ cosmomc_kde/pl18_relike_tanh_tau_dz0p5_1D_direct_vs_fortran_kde.png}
\caption{DEBUGGING - tanh dz = 0.5 for all curves. Same as above, but only keeping some curves for clarity.)
}
\label{fig:}
\end{figure}
